Ice-shelf ocean boundary layer dynamics from large-eddy simulations

### 2021-06-29 main.tex
Updates from Overleaf

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
    \end{minipage}
    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
    \end{minipage}
    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations. Y-axis limits differ between panels, with the black curve representing the same simulation in all panels.}
    \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}
    \newline\includegraphics[width=0.33\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period. (a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
    \label{fig:dT_profiles}
    % change colorbar label to \theta_\infty
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \newline
    \includegraphics[width=0.3\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period. (a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope). The black curve is common to both sets of simulations (see Figure \ref{fig:dT_profiles}).}
    \label{fig:dslope_profiles}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_46h_tav13_z_profile.png}    
    \end{minipage}
    \newline
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_46h_tav13_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_46h_tav13_z_profile.png}
    \end{minipage}
    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period. (b) Shear production. (c) Buoyancy production. The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted. (d) TKE transport. Positive denotes production, negative destruction. Note that the x-axis scales differ between panels.}
    \label{fig:tke_budget}
    % Change x-axis label for buoyancy production terms
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
    \end{minipage}
    \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations. Y-axis limits differ between panels, with the black curve representing the same simulation in all panels.}
    \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period. (a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
    \label{fig:dT_profiles}
    % change colorbar label to \theta_\infty
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period. (a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope). The black curve is common to both sets of simulations (see Figure \ref{fig:dT_profiles}).}
    \label{fig:dslope_profiles}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
    \end{minipage}
    \newline
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period. (b) Shear production. (c) Buoyancy production. The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted. (d) TKE transport. Positive denotes production, negative destruction. Note that the x-axis scales differ between panels.}
    \label{fig:tke_budget}
    % Change x-axis label for buoyancy production terms
\end{figure}
